Clustering of Distributions on 1-Dimensional Manifolds

### 2021-09-29 scratch/distributions-on-1d-manifolds.Rmd
typo

\begin{theorem}
\ref{thm:generalized}
Let $X_1, ..., X_n \iid F$ with support $[0, 1]$, and suppose $f(x)$ is continuous and $f(x) \geq a > 0$ everywhere on the support. 
Let $D_i = X_{(i+1)} - X_{(i)}$. 
Then for any $\epsilon > 0$, there exists $N \in \mathbb{N}$ such that $P(\max_i D_i < \delta) \geq 1 - \epsilon$ when $n > N$.
\end{theorem}

@@

\begin{theorem}
\ref{thm:multidim}
Let $X_1, ..., X_n \iid F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $E_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon \eta}{\log (1 - \frac{a \eta^r}{r^{r / 2}})} \bigg)$ such that $P(E_n) > 1 - \epsilon$ when $n \geq N$.
\end{theorem}

>>>>

\begin{theorem}
\label{thm:generalized}
Let $X_1, ..., X_n \iid F$ with support $[0, 1]$, and suppose $f(x)$ is continuous and $f(x) \geq a > 0$ everywhere on the support. 
Let $D_i = X_{(i+1)} - X_{(i)}$. 
Then for any $\epsilon > 0$, there exists $N \in \mathbb{N}$ such that $P(\max_i D_i < \delta) \geq 1 - \epsilon$ when $n > N$.
\end{theorem}

@@

\begin{theorem}
\label{thm:multidim}
Let $X_1, ..., X_n \iid F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $E_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon \eta}{\log (1 - \frac{a \eta^r}{r^{r / 2}})} \bigg)$ such that $P(E_n) > 1 - \epsilon$ when $n \geq N$.
\end{theorem}

### 2021-09-29 scratch/distributions-on-1d-manifolds.tex
typo

\begin{theorem}
\ref{thm:generalized}
Let $X_1, ..., X_n \stackrel{\mathrm{iid}}{\sim}F$ with support $[0, 1]$, and suppose $f(x)$ is continuous and $f(x) \geq a > 0$ everywhere on the support. 
Let $D_i = X_{(i+1)} - X_{(i)}$. 
Then for any $\epsilon > 0$, there exists $N \in \mathbb{N}$ such that $P(\max_i D_i < \delta) \geq 1 - \epsilon$ when $n > N$.
\end{theorem}

@@

\begin{theorem}
\ref{thm:multidim}
Let $X_1, ..., X_n \stackrel{\mathrm{iid}}{\sim}F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $E_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon \eta}{\log (1 - \frac{a \eta^r}{r^{r / 2}})} \bigg)$ such that $P(E_n) > 1 - \epsilon$ when $n \geq N$.
\end{theorem}

>>>>

\begin{theorem}
\label{thm:generalized}
Let $X_1, ..., X_n \stackrel{\mathrm{iid}}{\sim}F$ with support $[0, 1]$, and suppose $f(x)$ is continuous and $f(x) \geq a > 0$ everywhere on the support. 
Let $D_i = X_{(i+1)} - X_{(i)}$. 
Then for any $\epsilon > 0$, there exists $N \in \mathbb{N}$ such that $P(\max_i D_i < \delta) \geq 1 - \epsilon$ when $n > N$.
\end{theorem}

@@

\begin{theorem}
\label{thm:multidim}
Let $X_1, ..., X_n \stackrel{\mathrm{iid}}{\sim}F$ with support $[0, 1]^r$, and $f(x) \geq a > 0$ everywhere on the support. 
Define $E_n$ as the event that an $\eta$-neighborhood graph constructed from the sample is connected. 
Then for any $\epsilon > 0$, there exists $N = O \bigg( \frac{\log \epsilon \eta}{\log (1 - \frac{a \eta^r}{r^{r / 2}})} \bigg)$ such that $P(E_n) > 1 - \epsilon$ when $n \geq N$.
\end{theorem}
